%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{MUWANGA DAVID RICHARD}}}} % First name
	
	\vspace{6pt}
	
	{\Large Medical Doctor $\sim$ Full Stack Developer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	\icon{Globe}{11}{\href{http://www.portifolio.medvase.com}{portfolio.com}}\\ 
    \icon{Phone}{11}{+256 7845 80305}\\
    \icon{MapMarker}{11}{Mbarara, Uganda}\\
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\icon{Envelope}{11}{\href{mailto:dmuwanga25@gmail.com}{dmuwanga25@gmail.com}}\\	
    \icon{Github}{11}{\href{https://github.com/Dr-Muwanga}{Dr-Muwanga}}\\
    \icon{LinkedinSquare}{11}{\href{https://ug.linkedin.com/in/muwanga-david-2a662096}{muwangadavid}}\\    
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Summary}
    Highly motivated and results-oriented self-taught Full-Stack Web Developer with a unique foundation in Medicine and Surgery (MBChB). Proven ability to rapidly acquire and apply complex technical knowledge, coupled with strong analytical and problem-solving skills honed through rigorous medical training. Passionate about building impactful web applications that bridge technology and healthcare, or contribute to any dynamic development team.
    
\cvsect{Skills}
        \textbf{Languages:}
        \thinspace
        JavaScript (ES6+), TypeScript, HTML5, CSS3, SQL
    \vspace{2mm}
    
        \textbf{Front-End:}
        \thinspace
        React, Next js, Redux/Context API, Tanstack Query, Responsive Design, RESTful APIs
    \vspace{2mm}
    
        \textbf{Back-End:}
        \thinspace
        Node.js, Express.js, PostgreSQL, MongoDB, RESTful API Development, Memcached, PgBouncer, Prisma ORM
    \vspace{2mm}
    
        \textbf{DevOps:}
        \thinspace
        Cloud Platforms (Digital Ocean), VPS configuration, CI/CD Github pipelines. 
    \vspace{2mm}
    
        \textbf{Others:}
        \thinspace
        Git, Docker, npm, Webpack, Babel, Testing (Jest), Nginx, Memcached, Pgbuncer, database replication

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
		{ React js \\ Node js \\ Express js }
		{Social App for medics}
		{\href{https://app.medvase.com}{app.medvase.com}}
		{A social app hosted on a VPS, built with react js frontend and backend built on node js and express js with postgresql database.
        Currently has few visitors but with notable traffic}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{09/2024 \\- present}
		{Self learning by doing}
		{Internet and artificial intelligence}
		{Working on my own project, full stack scaled social media application with users and activity. Improving it daily through research, trial and error and artificial intelligence prompt engineering}
        
    \entry
		{04/2023 \\- 08/2024}
		{CS101: Introduction to Computer Science I}
		{Saylor Academy}
		{Understanding the fundamentals of computer science including history of computers, nomenclature in computer science and object oriented programming. I also got the fundamentals of Java }
        
    \entry
		{04/2023 \\- 06/2024}
		{Professional Certificate}
		{Online school Freecodecamp.org}
		{Acquired foundational information in HTML, CSS JavaScript and react js its framework. I also learned the basics of SQL and NoSQL. I also learned API setup with Node.js and Express.js, authentication, database setup, and integration}
        
	\entry
		{08/2016 \\- 05/2021}
		{Bachelors of Medicine and Bachelors of Surgery}
		{Mbarara University of Science and Technology}
		{I acquired clinical and leadership skills throughout the training process and also sharpened my problem-solving skills and ability to learn, unlearn, and relearn fast.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
        {09/2024 \\- present}
		{Social Media App for medical practitioners}
		{\href{https://app.medvase.com}{app.medvase.com}}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item {A social app allowing collaboration among medical practitioners in Africa, hosted on a VPS and fully functional.}
            \item {Built with react js on the frontend and Node js and Express js on the backend with postgresql database.}
            \item {Memcached for cache layer to reduce database traffic, pgbouncer to manage postgres connection pool, logical replication and HAProxy to ensure high availability}
        \end{itemize} 
        % \texttt{SQL} \slashsep \texttt{Excel}
        }
	\entry
		{04/2023 \\- present}
		{Medical Officer}
		{Pentagon Medical Centre}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Conducting comprehensive patient assessments, including medical history, physical examinations, and diagnostic tests working on over 80 patients per month of all age groups and gender.
            \item Formulating and implementing evidence-based treatment plans for patients with various medical conditions and surgical conditions.
            \item Collaborating with other healthcare departments like laboratory, imaging and pharmacy to provide comprehensive patient-centered care.
        \end{itemize} 
        % \texttt{SQL} \slashsep \texttt{Excel}
        }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
	\cvsect{Languages}
    \vspace{-6pt}
    
    \hspace{5mm} \textbf{English} - Proficient, \textbf{Luganda} - Proficient, \textbf{Runyankole} - Proficient, \textbf{Kiswahili} - Beginner

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------
% \vspace{2pt}
% 	\cvsect{References}
%     \vspace{-6pt}
    
%     \hspace{5mm} \textbf{English} - Proficient, \textbf{Luganda} - Proficient, \textbf{Runyankole} - Proficient, \textbf{Kiswahili} - Beginner

%----------------------------------------------------------------------------------------

\end{document}